---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# loop

*{loop}* contains two functions, 
`loop` unifies `lapply` and `Map`, `loop2` unifies `sapply` and `mapply`.

Both support a dollar notation so that we can leverage the autompletion of
function arguments. Arguments to be looped on are prefixed with `+`.

```{r}
library(loop)
loop(rep)(+11:12, 2)   # rather than `lapply(11:12, rep, 2)`
loop$rep(+11:12, 2)    # same thing, but we benefit from autocomplete
loop$rep(+11:12, +1:2) # rather than `Map(rep, 11:12, 1:2)`

# rather than `Map(function(...) rep(..., each =2), 11:12, 1:2)` :
loop$rep(+11:12, +1:2, each = 2)

l <- list(iris, cars)
loop2$nrow(+l) # rather than `sapply(l, nrow)`

# we can loop on nested "plussed" arguments too
loop$mean(c(+11:12,+1:2))
```

## Installation

Install with :

``` r
remotes::install_github("moodymudskipper/loop")
```

## Why ?

We get used to the apply functions, but : 

* They're hard to grasp at first
* No way to leverage the applied function's autocomplete
* The IDE highlights the apply function, not the applied function
* No need to shuffle the arguments when going from `lapply` to `Map` or `sapply` to `mapply`
* Much more compact to use constant arguments with `Map` and `mapply`
* I believe its more intuitive to have the applied function first
